---
title: "Aneurismi"
output:
  pdf_document: default
  html_notebook: default
---

# Allelic variants (control vs patients)
Single allelic variants frequency in patients group compared to healthy people
Reference: Table 1

## CYP2A6*2
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1 # To avoid p-value = 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6*B2
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6*14
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
# Allelic combinations (control vs patients)
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic-combinations.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
# Clinical features in patients
## CYP2A6 2 - singolo vs multiplo 
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2 - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 2 - sangunanti vs non sanguinanti
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2 - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 2 - fumo vs non fumo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2 - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 B2 - singolo vs multiplo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2 - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 B2 - sangunanti vs non sanguinanti
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2 - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 B2 - fumo vs non fumo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2 - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 14 - singolo vs multiplo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14 - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 14 - sangunanti vs non sanguinanti
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14 - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable)
```
## CYP2A6 14 - fumo vs non fumo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14 - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Allelic combinations - multiplo vs non multiplo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic_combinations - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Allelic combinations - sangunanti vs non
````{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic_combinations - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Allelic combinations - fumo vs non fumo
````{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic_combinations - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```


## Smoke + SAH vs No smoke + SAH
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - sah - smoke - nosmoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Smoke + NOSAH vs No smoke + NOSAH
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - no sah - smoke - nosmoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```