---
title: "Aneurismi"
output:
  pdf_document: default
  html_notebook: default
---

# Single allelic variants frequency in patients group compared to healthy people
Reference: Table 1

## CYP2A6*2
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1 # To avoid p-value = 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6*B2
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6*14
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
# Allelic combinations frequency in patients group compared to healthy people
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic-combinations.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
# Clinical features in patients
## CYP2A6 2 - singolo vs multiplo 
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2 - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 2 - sangunanti vs non sanguinanti
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2 - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 2 - fumo vs non fumo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 2 - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 B2 - singolo vs multiplo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2 - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 B2 - sangunanti vs non sanguinanti
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2 - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 B2 - fumo vs non fumo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 B2 - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 14 - singolo vs multiplo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14 - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## CYP2A6 14 - sangunanti vs non sanguinanti
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14 - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable)
```
## CYP2A6 14 - fumo vs non fumo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - CYP2A6 14 - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Allelic combinations - multiplo vs non multiplo
```{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic_combinations - multipli.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Allelic combinations - sangunanti vs non
````{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic_combinations - sah.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Allelic combinations - fumo vs non fumo
````{r}
filepath = "/home/frpnz/Projects/aneurismi/aneurismi_fumo - allelic_combinations - smoke.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 2
print(ctable)
fisher.test(ctable, alternative="two.sided")
```

#  Single polymorphisms and combinations correlation with IA rupture and smoking habits
Reference Table 4
## Smoke + SAH vs No smoke + SAH
## CYP2A6 2
```{r}
filepath = "aneurismi_fumo - sah - smoke - nosmoke - CYP2A6 2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Smoke + SAH vs No smoke + SAH
## CYP2A6 B2
```{r}
filepath = "aneurismi_fumo - sah - smoke - nosmoke - CYP2A6 B2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```

## Smoke + SAH vs No smoke + SAH
## CYP2A6 14
```{r}
filepath = "aneurismi_fumo - sah - smoke - nosmoke - CYP2A6 14.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Smoke + NOSAH vs No smoke + NOSAH
## CYP2A6 2
```{r}
filepath = "aneurismi_fumo - no sah - smoke - nosmoke - CYP2A6 2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Smoke + NOSAH vs No smoke + NOSAH
## CYP2A6 B2
```{r}
filepath = "aneurismi_fumo - no sah - smoke - nosmoke - CYP2A6 B2.csv"
dat = read.csv(filepath)
ctable <- table(dat)
ctable = ctable + 1
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Smoke + NOSAH vs No smoke + NOSAH
## CYP2A6 14
Fisher's exact test is appropriate only for tables, or parts of tables, with two rows and two columns that contain values (for example, a nested section of a larger table may be valid for this test). Rows and columns with no respondent data are ignored by the test, so a table with two rows and two columns may not be valid if, for example, one of the rows has no data. Conversely, a table with three rows and two columns may be suitable for the test if one of the rows has no data.
You can use this test on its own or in addition to the chi-square test. If you request the chi-square test and Fisher's exact test on the same table, a single chi-square column is used to display the results for both tests. If you request Fisher's exact test on a table that does not meet the requirements, it is not carried out.
The value returned by Fisher's exact test is the two-tailed p value, which does not distinguish between significantly high and significantly low results.

Serve aggiungere CT 0 nel dataframe
```{r}
filepath = "aneurismi_fumo - no sah - smoke - nosmoke - CYP2A6 14.csv"
dat = read.csv(filepath)
ctable <- table(dat)
print(ctable)
fisher.test(ctable, alternative="two.sided")
```
## Smoke + NOSAH vs No smoke + NOSAH
## Allelic combinations
```{r}
filepath = "aneurismi_fumo - no sah - smoke - nosmoke - allelic-comb.csv"
dat <- read.csv(filepath, header=TRUE, sep=",", row.names=1)
fisher.test(dat, alternative="two.sided")
```
## Smoke + SAH vs No smoke + SAH
## Allelic combinations
```{r}
filepath = "aneurismi_fumo - sah - smoke - nosmoke - allelic-comb.csv"
dat <- read.csv(filepath, header=TRUE, sep=",", row.names=1)
fisher.test(dat, alternative="two.sided")
```
## Bleeding and smoking in AA-AG-CC polymorphisms combination group
```{r}
filepath = "bleeding_smoking_in_AA-AG-CC.csv"
dat <- read.csv(filepath, header=TRUE, sep=",", row.names=1)
fisher.test(dat, alternative="two.sided")
```